---
title: "CPDR_manuscript"
author: "Peter Ching-Tze Ip$^{(}*,1}$, Thomas Avino$^{*,1}$, Judy Polakoff$^{*,1}$, Sandy Kwong$^{*,1}$, Mark Damesyn$^{*,1}$"
date: "April 2020"
output: 
pdf_document:
  fig_caption: yes
  fig_height: 5
  fig_width: 5
  keep_tex: yes
  md_extensions: +implicit_figures
word_document:
  fig_caption: yes
  fig_height: 5
  fig_width: 5
  md_extensions: +implicit_figures
  reference_docx: aje-word-style.docx
header-includes: \usepackage{setspace}\doublespacing
csl: nature.csl
bibliography: ca-parkinsons_monitr.bib
    
---
Files for style csl files can be located <https://github.com/citation-style-language/styles> or for additional guides <https://citationstyles.org>

```{r global-options, include=FALSE}

knitr::opts_chunk$set(fig.width=7.5, fig.height = 5, fig.path = 'figs/',
                      echo = FALSE, warning = FALSE, message = FALSE,
                      dev = "pdf")

my_round = function(x, k) format(round(x, k), nsmall = k)


```

```{r load-results}

#library(caPDmonitr)
library(gridExtra)
library(ggplot2)
library(broom)
library(scales)
library(knitr)
theme_set(theme_bw())
data("cpdr_index")
source('../')


```


\

<!--\begingroup \small

\vspace{10em} -->


#### Author Affiliations
1. California Department of Public Health, Sacramento, California, USA
2. University of California, Los Angeles, California, USA
3.

*Correspondence to Peter.Ip@cdph.ca.gov

\

<!-- \endgroup-->
<!-- \clearpage-->

<!-- \clearpage-->


# Introduction

# Methods

### Estimating... 

### Modeling...

### Data Availability

We developed open-source software, including a freely-available web application at [https://](https://). The source code for the web app, the data for the analyses, and the code to reproduce this manuscript itself are freely availabe online under, with a static version in an open-access digital library [@Peter:2020x]. All analyses were run in `r R.version.string`.[@rcoreteam]. These tools enable others to easily implement our model and reproduce our results.

# Results

### Measure Estimates

```{r figure1-demographic, fig.path='static-figures/', fig.show = 'hide', fig.height = 5, cache = FALSE, eval = TRUE, dev = 'tiff'}

data(cpdr_index)

grid.arrange(something
             , arrangeGrob(, , , heights = c(0.32, 0.32, 0.36))
             , ncol = 2
             )


```

```{r somekinaplots, fig.show = 'hide', cache = FALSE}


## making plots

```




```{r , echo=FALSE}

```

# Discussion


# Acknowledgements

# Author Contributions

# Competing Financial Interests

# Tables


<!-- \clearpage-->

# Figure captions



\
<!-- \clearpage-->

# Bibliography


<!-- \clearpage-->
